---
title: "Priyanka's script"
output: html_document
---

# Load libraries and read in data
```{r}
library(tidyverse) # for everything else!
library(lubridate) # for dates!
library(fs)
```

# Create function to calculate variability

I've rewritten that other guy's function to instead just calculate this via tibble-wrangling :)

```{r}
calc_tRMSSD <- function(mood_data, timestamp_data){
  if (length(mood_data) < 2){
    return(NA)
  } else {
  
  # create tibble and make sure it's arranged by timestamp
  data_calc <- tibble(
    mood = mood_data,
    timestamp = timestamp_data
  ) %>% 
    arrange(timestamp)
  
  # get the difference in mood and time between days
  data_calc <- data_calc %>% 
    mutate(dtime = timestamp - lag(timestamp),
           dmood = mood - lag(mood)) %>% 
    filter(!is.na(dmood)) %>% 
    mutate(dtime = as.numeric(dtime))
  
  # calculate the tRMSSD value
  sqrt(1/nrow(data_calc)*sum((data_calc$dmood/data_calc$dtime)^2))
  }
}

```

## Actigraphy data
### Read in data
We're going to read in the calender_date as a character, because the timezone actually changes at some point and that makes the dates move! And we drop that entirely BECAUSE it makes it seem as if there were 23 hours from one measurement to the next etc but there isnt and it also makes it seem as if there were two measurements on the same date when that wasn't the case.

```{r, message=FALSE}
# get the csv files in a named vector
participant_data <- list.files(path = "data/raw/Actigraphy", pattern = "actigraphy.csv$", full.names = TRUE) %>% 
  set_names()


my_read <- function(filepath){
  read_csv(filepath, col_types = list(
    id = col_character(),
    calender_date = col_character()
  ))
}

# read them in and put in a data frame
raw_data_acti <- map_dfr(participant_data, my_read, .id = "csv_file")

# clean it up
raw_data_acti_clean <- raw_data_acti %>% 
  mutate(participant_id = str_extract(path_file(csv_file), "c\\d+")) %>% 
  select(-csv_file) %>% 
  relocate(participant_id)

```

### Clean data
We are 

- adding columns for the date, week, weekday, and adds a numeric timestamp (this just as the date as a number - it's probably number of days since 1 jan 1970 or something to that effect! :)  )
- for each participant, we count the number of days from they started, and then the number of corresponding weeks
- removing entries that are NA for the RA column

```{r}
acti_data <- raw_data_acti_clean %>% 
  mutate(calender_date = str_sub(calender_date, 1, -6), # strip away the time zone information
         calender_date = ymd_hms(calender_date),
         date = date(calender_date),
         date_as_number = as.numeric(date),
         weekday = wday(date, label = TRUE),
         year = year(date)) %>% 
  group_by(participant_id) %>% 
  mutate(days_relative_to_first_measurement = date_as_number - min(date_as_number),
         weeks_count_from_start = floor(days_relative_to_first_measurement / 7) + 1) %>% 
  filter(across(c(L5_onset, L5_activity, M10_onset, M10_activity, RA), ~!is.na(.))) %>%  # drop rows with no measurements!
  distinct() %>% # drop duplicate rows
  relocate(weeks_count_from_start, calender_date, date, weekday)

```

### Calculate tRMSSD
#### By participant and week
So this here below groups by week (a week is Mon-Sun) and participant id and then just calculates the tRMSSD 

```{r}
tRMSSD_actigraphy <- acti_data %>% 
  group_by(participant_id, weeks_count_from_start) %>% 
  summarise(across(c(L5_onset, L5_activity, M10_onset, M10_activity, RA), ~ calc_tRMSSD(.x, date_as_number))) %>%  
  rename_with(.cols = -c(participant_id, weeks_count_from_start), ~str_c("tRMSSD_", .)) %>% 
  arrange(participant_id, weeks_count_from_start)

write_csv(tRMSSD_actigraphy, "data/processed/tRMSSD_actigraphy.csv")
```

#### By participant only
```{r}
tRMSSD_actigraphy_participant_overall <- acti_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(L5_onset, L5_activity, M10_onset, M10_activity, RA), ~ calc_tRMSSD(.x, date_as_number))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("tRMSSD_", .)) %>% 
  arrange(participant_id)

write_csv(tRMSSD_actigraphy_participant_overall, "data/processed/tRMSSD_actigraphy_by_participant.csv")
```

### Calculate averages
#### By participant and week

```{r}
mean_actigraphy <- acti_data %>% 
  group_by(participant_id, weeks_count_from_start) %>% 
  summarise(across(c(L5_onset, L5_activity, M10_onset, M10_activity, RA), ~ mean(.x, na.rm = TRUE))) %>%  
  rename_with(.cols = -c(participant_id, weeks_count_from_start), ~str_c("average_", .)) %>% 
  arrange(participant_id, weeks_count_from_start)

write_csv(mean_actigraphy, "data/processed/mean_actigraphy.csv")
```

#### By participant only
```{r}
mean_actigraphy_participant_overall <- acti_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(L5_onset, L5_activity, M10_onset, M10_activity, RA), ~ mean(.x, na.rm = TRUE))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("average_", .)) %>% 
  arrange(participant_id)

write_csv(mean_actigraphy_participant_overall, "data/processed/mean_actigraphy_by_participant.csv")
```


### Visualise actigraphy data
#### Join the group information

So in order to do this we want the information about the condition they were in! Yay!

We join with their group and then we drop the ones who don't have a group (there's like 4 of them - these are ppl who dropped out or were otherwise excluded)

```{r}
condition_info_acti <- read_csv("data/COMET_group_acti.csv") %>% 
  select(-`Participant ID`) %>% 
  mutate(Group = if_else(Group == 2, "low MDQ", "high MDQ")) %>% 
  rename(participant_id = ID)

tRMSSD_acti_w_group <- tRMSSD_actigraphy %>% 
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 

mean_acti_w_group <- mean_actigraphy %>%
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 
```

#### Make it long!

```{r}
tRMSSD_acti_w_group <- tRMSSD_actigraphy %>% 
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 

wide_scores_acti <- tRMSSD_acti_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  pivot_wider(names_from = weeks_count_from_start, values_from = c(tRMSSD_L5_onset, tRMSSD_L5_activity, tRMSSD_M10_onset, tRMSSD_M10_activity, tRMSSD_RA))


write_csv(wide_scores_acti, "data/processed/wide_scores_acti.csv")

#Same now for averages:
wide_scores_mean_acti <- mean_acti_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  pivot_wider(names_from = weeks_count_from_start, values_from = c(average_L5_onset, average_L5_activity, average_M10_onset, average_M10_activity, average_RA))

write_csv(wide_scores_mean_acti, "data/processed/wide_scores_mean_acti.csv")

```

#### Visualise the shit out of it
We exclude weeks after weeek 10

```{r}
tRMSSD_acti_weeks <- tRMSSD_acti_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  mutate(weeks_count_from_start = factor(weeks_count_from_start))

#Same now for averages:
mean_acti_weeks <- mean_acti_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  mutate(weeks_count_from_start = factor(weeks_count_from_start))
```

And NOW we can actually visualise it! Yay!

### Visualise tRMSSD acti data

#### Naive line graph across EVERYTHING for RA

```{r}
tRMSSD_acti_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = tRMSSD_RA, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id))
```

Let's make a similar one where we have facets for each of the measures.

We need a wrangling step first

```{r}
tRMSSD_acti_long <- tRMSSD_acti_weeks %>% 
  pivot_longer(-c(participant_id, Group, weeks_count_from_start)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "tRMSSD_"))

tRMSSD_acti_long %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = value, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~measure, scales = "free")
```

#### do the averages (with standard error of the mean)

```{r}
tRMSSD_acti_aves <- tRMSSD_acti_long %>% 
  group_by(Group, weeks_count_from_start, measure) %>% 
  summarise(ave_tRMSSD = mean(value, na.rm = TRUE),
            sd_tRMSSD = sd(value, na.rm = TRUE),
            se_tRMSSD = sd_tRMSSD/sqrt(n()))
  

tRMSSD_acti_plot <- tRMSSD_acti_aves %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = ave_tRMSSD, color = Group) +
    geom_point(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = Group)) +
    geom_errorbar(aes(ymin = ave_tRMSSD - se_tRMSSD, ymax = ave_tRMSSD + se_tRMSSD), width = 0.5, alpha = 0.8) +
    facet_wrap(~measure, scales = "free") +
    theme_minimal() +
    labs(title = "Variability in Actigraphy scores across weeks", x = "Week number", y = "Mean tRMSSD") 

tRMSSD_acti_plot
    
ggsave(plot = tRMSSD_acti_plot, "tRMSSD_acti_plot.png", height = 5, width = 8) 

  
```



#### Naive line graph w facets
```{r}
tRMSSD_acti_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = tRMSSD_RA, color = participant_id) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~Group)
```

#### Boxplot for overall tRMSSD
```{r}

tRMSSD_acti_overall_w_group <- tRMSSD_actigraphy_participant_overall %>% #join group info
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 

tRMSSD_acti_overall_long <- tRMSSD_acti_overall_w_group %>% #data wrangling - make long version of overall acti tRMSSD
  pivot_longer(-c(participant_id, Group)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "tRMSSD_"))

tRMSSD_acti_overall_w_group
tRMSSD_acti_overall_long

tRMSSD_acti_box_plot <- tRMSSD_acti_overall_long %>%
  ggplot() +
    aes(x = measure, y = value, fill = Group) +
    geom_boxplot(lwd=0.7, width=1.4, outlier.color = NA) +
    #scale_y_continuous(breaks = seq(0, 6, 0.5), limits = c(0, 6)) +
    theme_minimal() +
    facet_wrap(~measure, scales = "free") +
    labs(title = "Variability in overall Actigraphy measures", x = "Actigraphy measure", y = "tRMSSD")
  
tRMSSD_acti_box_plot

ggsave(plot = tRMSSD_acti_box_plot, "tRMSSD_acti_box_plot.png", height = 4, width = 7)
  
  
```

### Visualise mean acti data

#### Naive line graph across EVERYTHING for RA

```{r}
mean_acti_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = average_RA, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id))
```

Let's make a similar one where we have facets for each of the measures.

We need a wrangling step first

```{r}
mean_acti_long <- mean_acti_weeks %>% 
  pivot_longer(-c(participant_id, Group, weeks_count_from_start)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "average_"))

mean_acti_long %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = value, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~measure, scales = "free")
```

#### do the averages across participants (with standard error of the mean)

```{r}
mean_acti_aves <- mean_acti_long %>% 
  group_by(Group, weeks_count_from_start, measure) %>% 
  summarise(ave_mean = mean(value, na.rm = TRUE),
            sd_mean = sd(value, na.rm = TRUE),
            se_mean = sd_mean/sqrt(n()))
  

mean_acti_plot <- mean_acti_aves %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = ave_mean, color = Group) +
    geom_point(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = Group)) +
    geom_errorbar(aes(ymin = ave_mean - se_mean, ymax = ave_mean + se_mean), width = 0.5, alpha = 0.8) +
    facet_wrap(~measure, scales = "free") +
    theme_minimal() +
    labs(title = "Absolute actigraphy scores across weeks", x = "Week number", y = "Mean actigraphy") 

mean_acti_plot
    
ggsave(plot = mean_acti_plot, "mean_acti_plot.png", height = 5, width = 8) 

  
```



#### Naive line graph w facets
```{r}
mean_acti_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = average_RA, color = participant_id) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~Group)
```

#### Boxplot for overall mean
```{r}

mean_acti_overall_w_group <- mean_actigraphy_participant_overall %>% #join group info
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 

mean_acti_overall_long <- mean_acti_overall_w_group %>% #data wrangling - make long version of overall mean acti 
  pivot_longer(-c(participant_id, Group)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "average_"))

mean_acti_overall_w_group
mean_acti_overall_long

mean_acti_box_plot <- mean_acti_overall_long %>%
  ggplot() +
    aes(x = measure, y = value, fill = Group) +
    geom_boxplot(lwd=0.7, width=1.4, outlier.color = NA) +
    #scale_y_continuous(breaks = seq(0, 6, 0.5), limits = c(0, 6)) +
    theme_minimal() +
    facet_wrap(~measure, scales = "free") +
    labs(title = "Overall average actigraphy measures", x = "Actigraphy measure", y = "Mean")
  
mean_acti_box_plot

ggsave(plot = mean_acti_box_plot, "mean_acti_box_plot.png", height = 4, width = 7)
  
  
```


## PANAS
### Read in data
```{r, message=FALSE}
# get the csv files in a named vector
participant_data_panas <- list.files(path = "data/raw/PANAS", pattern = "PANAS.csv$", full.names = TRUE) %>% 
  set_names()

# read them in and put in a data frame
raw_data_panas <- map_df(participant_data_panas, read_csv, .id = "csv_file")

# clean it up
raw_data_panas_clean <- raw_data_panas %>% 
  mutate(participant_id = str_extract(path_file(csv_file), "c\\d+")) %>% 
  select(-csv_file) %>% 
  relocate(participant_id)
```

### Clean data
We are 

- adding columns for the date, week, weekday, and adds a numeric timestamp (this just as the date as a number - it's probably number of days since 1 jan 1970 or something to that effect! :)  )
- for each participant, we count the number of days from they started, and then the number of corresponding weeks

```{r}
panas_data <- raw_data_panas_clean %>% 
  mutate(date_time = str_c(testdate, testtime, sep = " "),
         date_time = dmy_hms(date_time),
         date = date(date_time),
         weekday = wday(date_time, label = TRUE),
         date_time_as_number = as.numeric(date_time),
         date_as_number = as.numeric(date)) %>% 
  group_by(participant_id) %>% 
  mutate(days_relative_to_first_measurement = date_as_number - min(date_as_number),
         weeks_count_from_start = floor(days_relative_to_first_measurement / 7) + 1) %>% 
  select(-c(testdate, testtime)) %>% 
  relocate(date_time, weekday, weeks_count_from_start)

```

### Calculate tRMSSD
#### By participant and week
So this here below groups by week (a week is Mon-Sun) and participant id and then just calculates the tRMSSD 

```{r}
tRMSSD_panas <- panas_data %>% 
  group_by(participant_id, weeks_count_from_start) %>% 
  summarise(across(c(pos, neg, sum), ~ calc_tRMSSD(.x, date_time_as_number))) %>% 
  rename_with(.cols = -c(participant_id, weeks_count_from_start), ~str_c("tRMSSD_", .)) %>% 
  arrange(participant_id, weeks_count_from_start)

tRMSSD_panas

write_csv(tRMSSD_panas, "data/processed/tRMSSD_panas.csv")

```
#### By participant only
```{r}
tRMSSD_panas_participant_overall <- panas_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(pos, neg, sum), ~ calc_tRMSSD(.x, date_as_number))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("tRMSSD_", .)) %>% 
  arrange(participant_id)

tRMSSD_panas_participant_overall

write_csv(tRMSSD_panas_participant_overall, "data/processed/tRMSSD_panas_by_participant.csv")
```

### Calculate averages
#### By participant and week
```{r}
mean_panas <- panas_data %>% 
  group_by(participant_id, weeks_count_from_start) %>% 
  summarise(across(c(pos, neg, sum), ~ mean(.x, na.rm = TRUE))) %>%  
  rename_with(.cols = -c(participant_id, weeks_count_from_start), ~str_c("average_", .)) %>% 
  arrange(participant_id, weeks_count_from_start)

write_csv(mean_panas, "data/processed/mean_panas.csv")
```

#### By participant only
```{r}
mean_panas_participant_overall <- panas_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(pos, neg, sum), ~ mean(.x, na.rm = TRUE))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("average_", .)) %>% 
  arrange(participant_id)

mean_panas_participant_overall

write_csv(mean_panas_participant_overall, "data/processed/mean_panas_by_participant.csv")
```


### Visualise PANAS data
#### Join the group information

So in order to do this we want the information about the condition they were in! Yay!

We join with their group and then we drop the ones who don't have a group (there's like 4 of them - these are ppl who dropped out or were otherwise excluded)

```{r}
condition_info_panas <- read_csv("data/COMET_group_panas.csv") %>% #this condition/group file excludes c15 variability outlier
#condition_info_panas <- read_csv("data/COMET_group.csv") %>% #this condition/group file includes c15 outlier
  select(-`Participant ID`) %>% 
  mutate(Group = if_else(Group == 2, "low MDQ", "high MDQ")) %>% 
  rename(participant_id = ID)

tRMSSD_panas_w_group <- tRMSSD_panas %>% 
  left_join(condition_info_panas) %>% 
  filter(!is.na(Group)) 

mean_panas_w_group <- mean_panas %>% 
  left_join(condition_info_panas) %>% 
  filter(!is.na(Group)) 


```

#### Make it long!

```{r}
tRMSSD_panas_w_group <- tRMSSD_panas %>% 
  left_join(condition_info_panas) %>% 
  filter(!is.na(Group)) 

wide_scores_panas <- tRMSSD_panas_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  pivot_wider(names_from = weeks_count_from_start, values_from = c(tRMSSD_pos, tRMSSD_neg, tRMSSD_sum))

write_csv(wide_scores_panas, "data/processed/wide_scores_panas.csv")

#Same now for averages:
wide_scores_mean_panas <- mean_panas_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  pivot_wider(names_from = weeks_count_from_start, values_from = c(average_pos, average_neg, average_sum))

wide_scores_mean_panas

write_csv(wide_scores_mean_panas, "data/processed/wide_scores_mean_panas.csv")

```

#### Visualise the shit out of it
We exclude weeks after week 10

```{r}
tRMSSD_panas_weeks <- tRMSSD_panas_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  mutate(weeks_count_from_start = factor(weeks_count_from_start))

#Same now for averages:
mean_panas_weeks <- mean_panas_w_group %>% 
  filter(weeks_count_from_start <= 10) %>% 
  mutate(weeks_count_from_start = factor(weeks_count_from_start))
```

And NOW we can actually visualise it! Yay!

### Visualise tRMSSD panas data

#### Naive line graph across EVERYTHING for panas pos

```{r}
tRMSSD_panas_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = tRMSSD_pos, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id))
```

Let's make a similar one where we have facets for each of the measures.

We need a wrangling step first

```{r}
tRMSSD_panas_long <- tRMSSD_panas_weeks %>% 
  pivot_longer(-c(participant_id, Group, weeks_count_from_start)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "tRMSSD_"))

tRMSSD_panas_long %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = value, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~measure, scales = "free")
```

#### do the averages (with standard error of the mean)

```{r}
tRMSSD_panas_aves <- tRMSSD_panas_long %>% 
  group_by(Group, weeks_count_from_start, measure) %>% 
  summarise(ave_tRMSSD = mean(value, na.rm = TRUE),
            sd_tRMSSD = sd(value, na.rm = TRUE),
            se_tRMSSD = sd_tRMSSD/sqrt(n()))
  
tRMSSD_panas_aves

tRMSSD_panas_plot <- tRMSSD_panas_aves %>% 
  filter(measure != "sum") %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = ave_tRMSSD, color = Group) +
    geom_point(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = Group)) + 
    geom_errorbar(aes(ymin = ave_tRMSSD - se_tRMSSD, ymax = ave_tRMSSD + se_tRMSSD), width = 0.5, alpha = 0.8) + 
    facet_wrap(~measure, scales = "free") +
    theme_minimal() +
    labs(title = "Variability in PANAS scores across weeks", x = "Week number", y = "Mean tRMSSD")

tRMSSD_panas_plot

ggsave(plot = tRMSSD_panas_plot, "tRMSSD_panas_plot.png", height = 4, width = 7)
```


#### Naive line graph w facets
```{r}
tRMSSD_panas_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = tRMSSD_pos, color = participant_id) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~Group)
```

#### Boxplot for overall tRMSSD
```{r}

tRMSSD_panas_overall_w_group <- tRMSSD_panas_participant_overall %>% #join group info
  left_join(condition_info_panas) %>% 
  filter(!is.na(Group)) 

tRMSSD_panas_overall_long <- tRMSSD_panas_overall_w_group %>% #data wrangling - make long version of overall panas tRMSSD
  pivot_longer(-c(participant_id, Group)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "tRMSSD_"))

tRMSSD_panas_overall_w_group
tRMSSD_panas_overall_long

tRMSSD_panas_box_plot <- tRMSSD_panas_overall_long %>%
  filter(measure != "sum") %>% 
  ggplot() +
    aes(x = measure, y = value, fill = Group) +
    geom_boxplot(lwd=0.7, width=1.4, outlier.color = NA) +
    scale_y_continuous(breaks = seq(0, 6, 0.5), limits = c(0, 6)) +
    theme_minimal() +
    #facet_wrap(~measure, scales = "free") +
    labs(title = "Variability in overall PANAS", x = "PANAS", y = "tRMSSD")
  
tRMSSD_panas_box_plot

ggsave(plot = tRMSSD_panas_box_plot, "tRMSSD_panas_box_plot.png", height = 4, width = 7)
  
  
```

### Visualise mean panas data

#### Naive line graph across EVERYTHING for RA

```{r}
mean_panas_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = average_pos, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id))
```

Let's make a similar one where we have facets for each of the measures.

We need a wrangling step first

```{r}
mean_panas_long <- mean_panas_weeks %>% 
  pivot_longer(-c(participant_id, Group, weeks_count_from_start)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "average_"))

mean_panas_long %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = value, color = Group) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~measure, scales = "free")
```

#### do the averages across participants (with standard error of the mean)

```{r}
mean_panas_aves <- mean_panas_long %>% 
  group_by(Group, weeks_count_from_start, measure) %>% 
  summarise(ave_mean = mean(value, na.rm = TRUE),
            sd_mean = sd(value, na.rm = TRUE),
            se_mean = sd_mean/sqrt(n()))
  

mean_panas_plot <- mean_panas_aves %>% 
  filter(measure != "sum") %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = ave_mean, color = Group) +
    geom_point(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = Group)) +
    geom_errorbar(aes(ymin = ave_mean - se_mean, ymax = ave_mean + se_mean), width = 0.5, alpha = 0.8) +
    facet_wrap(~measure, scales = "free") +
    theme_minimal() +
    labs(title = "Absolute PANAS scores across weeks", x = "Week number", y = "Mean PANAS") 

mean_panas_plot
    
ggsave(plot = mean_panas_plot, "mean_panas_plot.png", height = 5, width = 8) 

  
```

#### Naive line graph w facets
```{r}
mean_panas_weeks %>% 
  ggplot() +
    aes(x = weeks_count_from_start, y = average_pos, color = participant_id) +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5) +
    geom_line(aes(group = participant_id)) +
    facet_wrap(~Group)
```

#### Boxplot for overall mean
```{r}

mean_panas_overall_w_group <- mean_panas_participant_overall %>% #join group info
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 

mean_panas_overall_long <- mean_panas_overall_w_group %>% #data wrangling - make long version of overall mean acti 
  pivot_longer(-c(participant_id, Group)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "average_"))

mean_panas_overall_w_group
mean_panas_overall_long

mean_panas_box_plot <- mean_panas_overall_long %>%
  filter(measure != "sum") %>% 
  ggplot() +
    aes(x = measure, y = value, fill = Group) +
    geom_boxplot(lwd=0.7, width=1.4, outlier.color = NA) +
    scale_y_continuous(breaks = seq(0, 15, 1), limits = c(0, 15)) +
    theme_minimal() +
    #facet_wrap(~measure, scales = "free") +
    labs(title = "Overall average PANAS", x = "PANAS", y = "Mean")
  
mean_panas_box_plot

ggsave(plot = mean_panas_box_plot, "mean_panas_box_plot.png", height = 4, width = 7)
  
```

## True Colours
### Read in data
```{r, message=FALSE}
# get the csv files in a named vector
# participant_data_true_colours <- list.files(path = "data/raw/True_Colours", pattern = "true_colours.csv$", full.names = TRUE) %>% 
  # set_names()

# read them in and put in a data frame
# raw_data_true_colours <- map_df(participant_data_true_colours, read_csv, .id = "csv_file")

# actually should read in true colours data separately for each questionnaire (?)

participant_data_true_colours_qids <- read_csv("data/raw/True_Colours/qids_true_colours.csv")
participant_data_true_colours_altman <- read_csv("data/raw/True_Colours/altman_true_colours.csv")
participant_data_true_colours_gad7 <- read_csv("data/raw/True_Colours/gad7_true_colours.csv")

```

### Clean data
Do all true colours questionnaires separately (QIDS, Altman, GAD-7)
```{r, message=FALSE}
id_info_true_colours <- read_csv("data/true_colours_id.csv") %>% 
  select(-`Participant_no`) %>% 
  rename(participant_id = ID)

# raw_data_true_colours_clean <- raw_data_true_colours %>%
#  select(-`csv_file`) %>% 
#  left_join(id_info_true_colours) %>%
#  relocate(participant_id)

# add participant id to raw qids data and filter out anyone without participant id (just first test row)
raw_data_true_colours_qids_clean <- participant_data_true_colours_qids %>%
  select(-`q1`, -`q2`, -`q3`, -`q4`, -`q5`, -`q6`, -`q7`, -`q8`, -`q9`, -`q10`, -`q11`, -`q12`, -`q13`, -`q14`, -`q15`, -`q16`) %>% 
  left_join(id_info_true_colours) %>%
  filter(!is.na(participant_id)) %>%
  relocate(participant_id)

# add participant id to raw altman data and filter out anyone without participant id (just first test row)
raw_data_true_colours_altman_clean <- participant_data_true_colours_altman %>%
  select(-`q1`, -`q2`, -`q3`, -`q4`, -`q5`) %>% 
  left_join(id_info_true_colours) %>%
  filter(!is.na(participant_id)) %>%
  relocate(participant_id)

# add participant id to raw gad7 data and filter out anyone without participant id (just first test row)
raw_data_true_colours_gad7_clean <- participant_data_true_colours_gad7 %>%
  select(-`q1`, -`q2`, -`q3`, -`q4`, -`q5`, -`q6`, -`q7`) %>% 
  left_join(id_info_true_colours) %>%
  filter(!is.na(participant_id)) %>%
  relocate(participant_id)

# clean time stamp info for qids data
qids_true_colours_data <- raw_data_true_colours_qids_clean %>%
  mutate(date_time = str_c(date_time),
         date_time = ymd_hms(date_time),
         date = date(date_time),
         weekday = wday(date_time, label = TRUE),
         date_time_as_number = as.numeric(date_time),
         date_as_number = as.numeric(date), 
         year = year(date)) %>% 
  group_by(participant_id) %>% 
  mutate(days_relative_to_first_measurement = date_as_number - min(date_as_number),
         weeks_count_from_start = floor(days_relative_to_first_measurement / 7) + 1) %>% 
  filter(across(c(summary), ~!is.na(.))) %>%  # drop rows with no measurements!
  distinct() %>% # drop duplicate rows
  relocate(date_time, weekday, weeks_count_from_start)


# clean time stamp info for altman data
altman_true_colours_data <- raw_data_true_colours_altman_clean %>%
  mutate(date_time = str_c(date_time),
         date_time = ymd_hms(date_time),
         date = date(date_time),
         weekday = wday(date_time, label = TRUE),
         date_time_as_number = as.numeric(date_time),
         date_as_number = as.numeric(date), 
         year = year(date)) %>% 
  group_by(participant_id) %>% 
  mutate(days_relative_to_first_measurement = date_as_number - min(date_as_number),
         weeks_count_from_start = floor(days_relative_to_first_measurement / 7) + 1) %>% 
  filter(across(c(summary), ~!is.na(.))) %>%  # drop rows with no measurements!
  distinct() %>% # drop duplicate rows
  relocate(date_time, weekday, weeks_count_from_start)


# clean time stamp info for gad7 data
gad7_true_colours_data <- raw_data_true_colours_gad7_clean %>%
  mutate(date_time = str_c(date_time),
         date_time = ymd_hms(date_time),
         date = date(date_time),
         weekday = wday(date_time, label = TRUE),
         date_time_as_number = as.numeric(date_time),
         date_as_number = as.numeric(date), 
         year = year(date)) %>% 
  group_by(participant_id) %>% 
  mutate(days_relative_to_first_measurement = date_as_number - min(date_as_number),
         weeks_count_from_start = floor(days_relative_to_first_measurement / 7) + 1) %>% 
  filter(across(c(summary), ~!is.na(.))) %>%  # drop rows with no measurements!
  distinct() %>% # drop duplicate rows
  relocate(date_time, weekday, weeks_count_from_start)

```

### Calculate tRMSSD
#### By participant only
There is only one true colours recording per week (per participant) so can only have overall (by participant) tRMSSD score
```{r}

# qids
tRMSSD_qids_true_colours_participant_overall <- qids_true_colours_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(summary), ~ calc_tRMSSD(.x, date_as_number))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("tRMSSD_qids_", .)) %>% 
  arrange(participant_id)

tRMSSD_qids_true_colours_participant_overall

write_csv(tRMSSD_qids_true_colours_participant_overall, "data/processed/tRMSSD_qids_true_colours_by_participant.csv")

# altman
tRMSSD_altman_true_colours_participant_overall <- altman_true_colours_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(summary), ~ calc_tRMSSD(.x, date_as_number))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("tRMSSD_altman_", .)) %>% 
  arrange(participant_id)

tRMSSD_altman_true_colours_participant_overall

write_csv(tRMSSD_altman_true_colours_participant_overall, "data/processed/tRMSSD_altman_true_colours_by_participant.csv")

# gad7
tRMSSD_gad7_true_colours_participant_overall <- gad7_true_colours_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(summary), ~ calc_tRMSSD(.x, date_as_number))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("tRMSSD_gad7_", .)) %>% 
  arrange(participant_id)

tRMSSD_gad7_true_colours_participant_overall

write_csv(tRMSSD_gad7_true_colours_participant_overall, "data/processed/tRMSSD_gad7_true_colours_by_participant.csv")

```

### Calculate averages
#### By participant only
```{r}

# qids
mean_qids_true_colours_participant_overall <- qids_true_colours_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(summary), ~ mean(.x, na.rm = TRUE))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("average_qids_", .)) %>% 
  arrange(participant_id)

mean_qids_true_colours_participant_overall

write_csv(mean_qids_true_colours_participant_overall, "data/processed/mean_qids_true_colours_by_participant.csv")

# altman
mean_altman_true_colours_participant_overall <- altman_true_colours_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(summary), ~ mean(.x, na.rm = TRUE))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("average_altman_", .)) %>% 
  arrange(participant_id)

mean_altman_true_colours_participant_overall

write_csv(mean_altman_true_colours_participant_overall, "data/processed/mean_altman_true_colours_by_participant.csv")

# gad7
mean_gad7_true_colours_participant_overall <- gad7_true_colours_data %>% 
  group_by(participant_id) %>% 
  summarise(across(c(summary), ~ mean(.x, na.rm = TRUE))) %>%  
  rename_with(.cols = -c(participant_id), ~str_c("average_gad7_", .)) %>% 
  arrange(participant_id)

mean_gad7_true_colours_participant_overall

write_csv(mean_gad7_true_colours_participant_overall, "data/processed/mean_gad7_true_colours_by_participant.csv")

```


### Visualise True Colours data
#### Join the group information

So in order to do this we want the information about the condition they were in! Yay!

We join with their group and then we drop the ones who don't have a group (there's like 4 of them - these are ppl who dropped out or were otherwise excluded)

```{r}
#condition_info_panas <- read_csv("data/COMET_group_panas.csv") %>% #this condition/group file excludes c15 variability outlier
condition_info_true_colours <- read_csv("data/COMET_group.csv") %>% #this condition/group file includes c15 outlier
  select(-`Participant ID`) %>% 
  mutate(Group = if_else(Group == 2, "low MDQ", "high MDQ")) %>% 
  rename(participant_id = ID)

# Join for qids
tRMSSD_qids_true_colours_w_group <- tRMSSD_qids_true_colours_participant_overall %>% 
  left_join(condition_info_true_colours) %>% 
  filter(!is.na(Group)) 

mean_qids_true_colours_w_group <- mean_qids_true_colours_participant_overall %>% 
  left_join(condition_info_true_colours) %>% 
  filter(!is.na(Group)) 

# Join for altman
tRMSSD_altman_true_colours_w_group <- tRMSSD_altman_true_colours_participant_overall %>% 
  left_join(condition_info_true_colours) %>% 
  filter(!is.na(Group)) 

mean_altman_true_colours_w_group <- mean_altman_true_colours_participant_overall %>% 
  left_join(condition_info_true_colours) %>% 
  filter(!is.na(Group)) 

# Join for gad7
tRMSSD_gad7_true_colours_w_group <- tRMSSD_gad7_true_colours_participant_overall %>% 
  left_join(condition_info_true_colours) %>% 
  filter(!is.na(Group)) 

mean_gad7_true_colours_w_group <- mean_gad7_true_colours_participant_overall %>% 
  left_join(condition_info_true_colours) %>% 
  filter(!is.na(Group)) 

```

#### Boxplot for overall tRMSSD
```{r}

# data wrangling - first join 3 true colours tRMSSD files together

tRMSSD_true_colours_overall <- cbind(tRMSSD_qids_true_colours_w_group, tRMSSD_altman_true_colours_w_group, tRMSSD_gad7_true_colours_w_group) 

write_csv(tRMSSD_true_colours_overall, "data/processed/tRMSSD_true_colours_by_participant.csv")

tRMSSD_true_colours_overall_long <- tRMSSD_true_colours_overall %>% #data wrangling - make long version of overall true colours tRMSSD
  pivot_longer(-c(participant_id, Group)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "tRMSSD_")) %>% 
  mutate(measure = str_remove(measure, "_summary"))

tRMSSD_true_colours_box_plot <- tRMSSD_true_colours_overall_long %>%
  ggplot() +
    aes(x = measure, y = value, fill = Group) +
    geom_boxplot(lwd=0.7, width=1.4, outlier.color = NA) +
    # scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1)) +
    theme_minimal() +
    facet_wrap(~measure, scales = "free") +
    labs(title = "Variability in overall True Colours scales", x = "True Colours", y = "tRMSSD")
  
tRMSSD_true_colours_box_plot

ggsave(plot = tRMSSD_true_colours_box_plot, "tRMSSD_true_colours_box_plot.png", height = 4, width = 7)
  
  
```

#### Boxplot for overall mean
```{r}

# data wrangling - first join 3 true colours average files together

mean_true_colours_overall <- cbind(mean_qids_true_colours_w_group, mean_altman_true_colours_w_group, mean_gad7_true_colours_w_group)

write_csv(mean_true_colours_overall, "data/processed/mean_true_colours_by_participant.csv")

mean_true_colours_overall_long <- mean_true_colours_overall %>% #data wrangling - make long version of overall true colours mean
  pivot_longer(-c(participant_id, Group)) %>% 
  rename(measure = name) %>% 
  mutate(measure = str_remove(measure, "average_")) %>% 
  mutate(measure = str_remove(measure, "_summary"))

mean_true_colours_box_plot <- mean_true_colours_overall_long %>%
  ggplot() +
    aes(x = measure, y = value, fill = Group) +
    geom_boxplot(lwd=0.7, width=1.4, outlier.color = NA) +
    # scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1)) +
    theme_minimal() +
    facet_wrap(~measure, scales = "free") +
    labs(title = "Overall average True Colours", x = "True Colours", y = "mean")
  
mean_true_colours_box_plot

ggsave(plot = mean_true_colours_box_plot, "mean_true_colours_box_plot.png", height = 4, width = 7)
```

#### Visualisations across weeks (for average only)
```{r}
week_true_colours_data = read.csv("data/weekly_true_colours_data.csv")

#condition_info_panas <- read_csv("data/COMET_group_panas.csv") %>% #this condition/group file excludes c15 variability outlier
condition_info_true_colours <- read_csv("data/COMET_group.csv") %>% #this condition/group file includes c15 outlier
  select(-`Participant ID`) %>% 
  mutate(Group = if_else(Group == 2, "low MDQ", "high MDQ")) %>% 
  rename(participant_id = ID)

week_true_colours_data_w_group <- week_true_colours_data %>%
  left_join(condition_info_panas) %>% 
  filter(!is.na(Group)) %>% 
  relocate(Group)

week_true_colours_data_w_group


```



# Other stuff
Here's some other stuff you wanted! :)

## actigraphy data
```{r}
# count number of weeks each participant has data from
acti_data %>% 
  distinct(participant_id, weeks_count_from_start) %>% 
  group_by(participant_id) %>% 
  summarise(num_weeks = n())

# count how many entries each participant has within a week
acti_data %>% 
  count(participant_id, weeks_count_from_start)
```

## panas data
```{r}
# count number of weeks each participant has data from
panas_data %>% 
  distinct(participant_id, weeks_count_from_start) %>% 
  group_by(participant_id) %>% 
  summarise(num_weeks = n())

# count how many entries each participant has within a week
panas_data %>% 
  count(participant_id, weeks_count_from_start)
```

## Take a look at files

```{r}

tRMSSD_actigraphy <- read_csv("data/processed/tRMSSD_actigraphy.csv")
view(tRMSSD_actigraphy)


```

# Join all week data together for LMMs

```{r}
tRMSSD_acti_lmm <- tRMSSD_acti_w_group %>%
  filter(weeks_count_from_start <= 10)
#write_csv(tRMSSD_acti_lmm, "data/processed/tRMSSD_acti_lmm.csv")

mean_acti_lmm <- mean_acti_w_group %>%
  filter(weeks_count_from_start <= 10)
#write_csv(mean_acti_lmm, "data/processed/mean_acti_lmm.csv")



tRMSSD_panas_w_group_acti <- tRMSSD_panas %>% # want to add acti group here to make same length 
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 

mean_panas_w_group_acti <- mean_panas %>% # want to add acti group here to make same length 
  left_join(condition_info_acti) %>% 
  filter(!is.na(Group)) 

tRMSSD_panas_lmm <- tRMSSD_panas_w_group_acti %>%
  filter(weeks_count_from_start <= 10)
#write_csv(tRMSSD_panas_lmm, "data/processed/tRMSSD_panas_lmm.csv")

mean_panas_lmm <- mean_panas_w_group_acti %>%
  filter(weeks_count_from_start <= 10)
#write_csv(mean_panas_lmm, "data/processed/mean_panas_lmm.csv")

all_week_data_acti <- cbind(mean_acti_lmm, tRMSSD_acti_lmm)
write_csv(all_week_data_acti, "data/processed/all_week_data_acti.csv") 

all_week_data_panas <- cbind(mean_panas_lmm, tRMSSD_panas_lmm)
write_csv(all_week_data_panas, "data/processed/all_week_data_panas.csv") 
```
